Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS J08354256-0819237 and 2MASS J18212815+1414010

### 2016-12-15 ms.tex
I added some more descriptions of the two parameter and one parameter MCMC runs I did.

\section{Color-Magnitude Diagram}
\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{color_mag.pdf}
\caption{Color-Magnitude diagram from \citet{dupuy2012ltparallax}. We added 2MASS J1821 and 2MASS J0835 using Simbad magnitudes and parallaxes.}\label{fig:CMD}
\end{centering}
\end{figure}

\section{Example Posterior Distributions}
\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{corner_example.pdf}
\caption{Example posterior distributions for an MCMC fit to the time series using Equation \ref{eq:cosfit} for the wavelength bin 1.08~$\mu$m.}\label{fig:postCosfit}
\end{centering}
\end{figure}

We also explore a 2 term sinusoidal fit:

\begin{equation}\label{eq:cosfit2term}
F(t) = A_1 \cos(2 \pi (t - t_1)/\tau) + A_2 \cos(4 \pi (t - t_2)/\tau) +  B t + C
\end{equation}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{corner_example.pdf}
\caption{Example posterior distributions for an MCMC fit to the time series using Equation \ref{eq:cosfit} for the wavelength bin 1.08~$\mu$m.}\label{fig:post2Cosfit}
\end{centering}
\end{figure}

>>>>

\section{Color-Magnitude Diagram}

Figure \ref{fig:CMD} shows the color magnitude diagram from the sample of brown dwarfs in \citet{dupuy2012ltparallax}, which includes 2MASS J0835-0819 but not 2MASS J1812+1414.
We highlight these two brown dwarfs to be contrasted with the rest of the population.

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{color_mag.pdf}
\caption{Color-Magnitude diagram from \citet{dupuy2012ltparallax}. We added 2MASS J1821-0819 and 2MASS J0835+1414 using Simbad magnitudes and parallaxes.}\label{fig:CMD}
\end{centering}
\end{figure}

\section{Example Posterior Distributions}

In Figure \ref{fig:postCosfit}, we show the posterior distributions of a sinusoidal model (Equation \ref{eq:cosfit}) fit to the data using \texttt{emcee} \citep{foreman-mackey2013emcee} for an example wavelength bin of 1.08~$\mu$m.
This wavelength bin is one of the high amplitude fits that is relatively unaffected by telluric contamination.
We impose priors on the amplitude $A_1$ so that it would be positive, $t_1$ would be less than the observation windows (to avoid multiple periodic solutions) and that the period $\tau$ would be between 0 and the observation window length.
The model parameters are close to Gaussian and the only visible correlation is between the time offset, $t_1$, and the rotation period $\tau$.

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{corner_example.pdf}
\caption{Example posterior distributions for an MCMC fit to the time series using Equation \ref{eq:cosfit} for the wavelength bin 1.08~$\mu$m.}\label{fig:postCosfit}
\end{centering}
\end{figure}

We also explore a 2 term sinusoidal fit with a second cosine function at twice the frequency:
\begin{equation}\label{eq:cosfit2term}
F(t) = A_1 \cos(2 \pi (t - t_1)/\tau) + A_2 \cos(4 \pi (t - t_2)/\tau) +  B t + C
\end{equation}
Now there are two amplitude parameters $A_1$ and $A_2$ and two time offset parameters $t_1$ and $t_2$.
Figure \ref{fig:model2Cosfit} shows the best fit compared to the data for this 2 term sinusoidal fit.
We assume the same priors as the 1 term sinusoidal fit with both $A_1$ and $A_2 > 0$.
The two term model appears visually to fit the data well.
The $\chi^2$ per degree of freedom is still 7.9, so it is not the expected 1.0.
However, the error bars are likely underestimated when using photon and read noise limits.

@@

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{corner_fit_2term.pdf}
\caption{Example posterior distributions for an MCMC fit to the time series using Equation \ref{eq:cosfit} for the wavelength bin 1.08~$\mu$m.}\label{fig:post2Cosfit}
\end{centering}
\end{figure}
